Revisiting~the~Classics: Online~RL~in~the~Programmable~Dataplane

### 2021-05-07 paper/paper.tex
Some diagram descriptions

@@

\begin{figure}
	\centering
	\includegraphics[keepaspectratio, width=0.9\linewidth]{figures/arch-with-p4}
	\caption{Architecture for an \approachshort{} agent on Netronome hardware, using 4 cores for parallel policy processing. (FIXME: redo in illustrator? Show CTXes, PISA, \Coopfw{} vs \Indfw{})\label{fig:netro-arch}}
\end{figure}

@@

\begin{figure*}
	\centering
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[keepaspectratio, width=0.9\linewidth]{figures/ind}
		\caption{\Indfw{} (offline throughput-optimal).\label{fig:single-and-parallel:single}}
	\end{subfigure}
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[keepaspectratio, width=0.9\linewidth]{figures/coop}
		\caption{\Coopfw{} (online-optimal).\label{fig:single-and-parallel:parallel}}
	\end{subfigure}
	\caption{\approachshort{}'s compute strategies scale to fit device capacity according to latency/throughput needs. ?? MAKE ME FOR REAL \label{fig:single-and-parallel}}
\end{figure*}

>>>>

\begin{figure}
	\centering
	\includegraphics[keepaspectratio, width=0.9\linewidth]{figures/arch-with-p4}
	\caption{\approachshort{} brings low-latency, online reinforcement learning directly to the dataplane. SoC- and NetFPGA-based SmartNIC devices expose spare compute---making in-situ, asynchronous processing and learning possible.\label{fig:netro-arch}}
\end{figure}

@@

@@

\begin{figure*}
	\centering
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[keepaspectratio, width=0.9\linewidth]{figures/ind}
		\caption{\Indfw{} (offline throughput-optimal). \emph{Workers} independently pull commands from and push state-action pairs to the environment (locking access to when updates must occur).\label{fig:single-and-parallel:single}}
	\end{subfigure}
\hspace{0.04\linewidth}
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[keepaspectratio, width=0.9\linewidth]{figures/coop}
		\caption{\Coopfw{} (online-optimal). A single \emph{controller} ... to many \emph{minion} threads, who operate on independent subtasks.\label{fig:single-and-parallel:parallel}}
	\end{subfigure}
	\caption{\approachshort{}'s compute strategies scale to fit device capacity according to latency/throughput needs.\label{fig:single-and-parallel}}
\end{figure*}
